---
title: "Proof of Concept"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{first-steps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r pkgs}
library(dplyr)
library(purrr)
library(sf)
library(packcircles)
library(ggplot2)
library(ishihara)
```


```{r setup}
library(ishihara)
```

Here's the goal:

1. Create a bunch of circles with `packcircles`.
2. Convert those circles to an SF object.
3. Pull in a vector font.
4. Convert that font into an SF object
5. Overlay the two SF objects and see where they intersect
6. Plot the circles that are intersected by the text
7. Change the colour palette in ggplot2 to see the impact of colourblindness


# 1. Create a bunch of circles

```{r}
circle_plate <- create_circle_plate()
```

# 2. Convert circles to an `sf` spatial object.

```{r}
circle_plate_sf <- cast_packing_poly(circle_plate)
```

# 3. Pull in a vector font (and resize the font)

```{r}
letter_s <- glyph("s") %>% font_rescale(circle_plate)
```

# 4. Convert that font into an SF object 

```{r}
letter_s_sf <- cast_font_sf(letter_s)
```

# 5. Overlay the two SF objects and see where they intersect

```{r}
overlayed_circle <- overlay_text_in_circle(circle_plate_sf, letter_s_sf)
```

# 6. plot the object

```{r plot-ishihara}
gg_ishihara <- ggplot(overlayed_circle) +
  geom_sf(aes(fill = in_text),
          colour = "white") +
  theme_void() +
  theme(legend.position = "none")
```

# 7. Change the colour palette in ggplot2 to see the impact of colourblindness

```{r plot-multiple-colours}
gg_ishihara + scale_fill_viridis_d()
```

